Malacology: A Programmable Storage System

### 2016-10-06 paper/paper.tex
paper: emphasize hooks and outline
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\usepackage{fullpage}
\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{amsmath}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{listings}

@@

\subsection{Cluster State Management}
\label{sec:mon}
\label{consistencyversioning-of-cluster-state}

@@

\label{services}

\begin{table}
\centering
\begin{tabular}{  l | l | l    }
\textbf{Service} & \textbf{Ceph Component} & \textbf{Used for...}  \\ \hline
Mantle  & RADOS    & policy durability \\
        & MON maps & policy versioning \\ \hline
ZLog    & Logical Storage & CORFU protocol  \\ 
        & MON maps & interface install \\ \hline
Seq.    & MDS file types & log management \\ 
        & MDS fault toler. & seq. fault toler. \\
\end{tabular}
\caption{To implement the Mantle and ZLog services, we leverage Ceph
components. Malacology uses these subsystems because they provide powerful
abstractions.}
\label{table:implementation}
\end{table}

>>>>

\usepackage{fullpage}
\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{amsmath}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

\subsection{Versioning: Cluster State Management}
\label{sec:mon}
\label{consistencyversioning-of-cluster-state}

@@

\label{services}
\begin{table}
\centering
\begin{tabular}{  l | l | l | l }
\textbf{Service} & \text{*} & \textbf{Malacology Hook} & \textbf{Used to...}  \\ \hline
Mantle           &          & Logical Storage  & implement metadata balancers \\
                 & \cmark   & Versioning       & agree on current balancer \\ 
                 & \cmark   & Capabilities     & control client write lock \\
                 &          & Durability       & persist/distribute policy logic \\\hline
ZLog             & \cmark   & Logical Storage  & implement CORFU protocol  \\ 
                 & \cmark   & Versioning       & agree on ZLog version \\
                 & \cmark   & Capabilities     & file types for log management \\
                 &          & Durability       & persist log entries \\ \hline
Seqr.            &          & Logical Storage  & load balancing \\
                 & \cmark   & Versioning       & fault tolerance \\
                 & \cmark   & Capabilities     & control client bursts \\ 
\end{tabular}
\caption{Because Mantle and ZLog are built on Malacology, they inherit the
robustness of the internal subsystems of the underlying storage stack.\\ For
the \text{*} column, the \cmark s are hooks contributed in this paper;
durability is provided by librados and Lua Policy (MDS) is already
published~\cite{sevilla:sc15-mantle}. }
\label{table:implementation}
\end{table}
